\documentclass{libtex/llncs}

\usepackage{url}
\usepackage{color}
\usepackage{paralist}
\usepackage{fancyvrb}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{subfig}
\usepackage{float}
\usepackage[nomove]{cite}
\usepackage{tabularx}
\usepackage[table]{xcolor}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{mdframed}
\usepackage{multirow}
%\usepackage[table,xcdraw]{xcolor}


\graphicspath{ {figures/} }


\newcommand{\new}[1]{{\color{blue}#1}}
\newcommand{\draft}[1]{{\color{red}#1}}
\long\def\comment#1{}
\newcommand{\q}[1]{\lq\lq{}{}#1\rq\rq{}{}}

\begin{document}

\title{
    Ranking Archived Documents for Structured Queries on Semantic Layers% and Time
    %Capturing Implicit User Search Preferences through Ranking Algorithms on Structured Data
}

\author{
    Vaibhav Kasturia \and
    Pavlos Fafalios \and
    Wolfgang Nejdl }

\institute{
    L3S Research Center, University of Hannover, Germany\\
    \email{\{kasturia, fafalios, nejdl\}@l3s.de} }



\maketitle


\begin{abstract}
Archived collections of documents (like newspaper and web archives)
serve as important information sources
in a variety disciplines, including Digital Humanities, Historical Science, and Journalism.
%for a variety of interested parties, such as historians, journalists and sociologists.
However, the absence of efficient and meaningful exploration methods
still remains a major hurdle in the way of turning them into usable sources of information.
Semantic Layers allow describing
and publishing metadata and semantic information about the archived documents in a standard format (RDF),
which in turn can be queried through a semantic query language (SPARQL).
This allows running advanced queries by combining
metadata of the documents (like publication date) and
content-based semantic information (like entities mentioned in the documents).
However, the results returned by structured queries
can be numerous and also they all equally match the query.
There is thus the need to rank the returned results in order to identify and promote the most important ones.
In this paper,
we formalize the problem of {\em ranking archived documents for structured queries},
we distinguish two main types of queries for this problem,
and we propose a baseline ranking model that jointly considers the following aspects:
i) the relativeness of documents to entities,
ii) the timeliness of documents, and
iii) the relations among the entities.
The results of an extensive experimental evaluation on a news archive are promising.
\end{abstract}



\section{Introduction}
%Digital archiving is the long-term electronic preservation and management
%of historical documents and assets in general.

Despite the increasing number of digital archives worldwide
(like newspaper and web archives), the absence of efficient and meaningful
exploration methods still remains the major bottleneck in the way of
turning them into usable information sources \cite{calhoun2014exploring}.
Semantic models try to solve this problem by offering the means
to describe metadata and semantic information
about a collection of archived documents in the standard RDF format.
A repository of such data, called Semantic Layer \cite{fafalios2017SemLayer},
allows running advanced queries which
combine metadata of the documents (like publication date) and
content-based semantic information (like entities mentioned in the documents).
As an example, we can access a Semantic Layer over a newspaper archive and
find articles of a specific time period discussing about a specific category of entities
(e.g., {\em philanthropists}) or about entities sharing some characteristics
(e.g., {\em lawyers born in Germany}).
Such advanced information needs can be directly expressed through structured (SPARQL) queries
or through user-friendly interactive interfaces
which transparently transform user interactions to SPARQL queries
(e.g., a faceted browsing interface \cite{tzitzikas2016faceted}).

However, the results returned by such queries can be numerous and
moreover they all equally match the query.
Thus, there arises the need for an effective method to rank the returned results
for discovering and promoting the most important ones.
As an example, when requesting articles from a news archive mentioning a specific entity,
some of the returned articles may be about that entity
while other articles may just mention the entity without it being their main topic.
Thus, an effective ranking method should
consider the different factors that affect the importance of documents to the information need,
relying at the same time only on the data
available in the semantic layer (without accessing documents' full contents).

Although there is a plethora of works on both
ranking archived documents for keyword-based queries
and ranking structured data (subjects and objects) in knowledge graphs,
the problem of ranking archived documents for structured queries in knowledge graphs
has not yet been recognized and studied.
In this paper, we address this gap by first introducing and formalizing this task
and then proposing a ranking model for the problem at hand.
The proposed model jointly considers the following aspects:
i) the {\em relativeness} of a document with respect to the entities of interest,
ii) the {\em timeliness} of document's publication date,
iii) the temporal {\em relatedness} of the entities of interest with other entities
mentioned in the document.
The idea is to promote documents that
mention the entities of interest many times,
that have been published in important (for the entities of interest) time periods, and that
mention many other entities co-occurring frequently
with the entities of interest in important time periods.
For example, in case we want to rank articles of 1990
discussing about {\em Nelson Mandela},
we want to favor articles that
i) mention {\em Nelson Mandela} multiple times in their text,
ii) have been published in important time periods for {\em Nelson Mandela}
(e.g., February 1990 since during that period he was released from prison), and
iii) mention other entities that seem to be important for {\em Nelson Mandela}
during important time periods
(e.g., {\em Frederik Willem de Klerk} who was
South Africa's State President in February 1990).

In a nutshell, in this paper we make the following contributions:
\begin{compactitem}
\item   We formulate and formalize the problem of ranking archived documents
        for structured queries over semantic layers.
\item   \draft{We proposed a ranking model for the problem at hand that ... ...}
\item   Due to lack of evaluation datasets for our problem, we have created
        a new ground truth dataset for a news archive which we make publicly available.
\item   \draft{The evaluation results show that the proposed ranking model ...}
\end{compactitem}
%For this problem, we should consider the different factors
%that affect the importance of a document to the information need,
%relying at the same time only on the data
%available in the semantic layer (without accessing documents' full contents).

\comment{====
    Archiving is the process of preservation of records
    permanently or for long-terms on grounds of their
    enduring cultural, evidentiary or historical value.
    As the web continues to grow we have records holding
    significant value being constantly produced
    and consumed every day. However, due to transient
    nature of the Web, most of these records produced
    become either lost or unavailable after a short period
    of time. Archives capture portions of these record
    collections for sociologists, historians and other interested
    parties for whom these collections are immensely valuable.

    Just as Archives contain historical records,
    in the same way Web Archives capture portions of the Web
    in order to preserve it for
    sociologists, historians, and other interested parties.
    For them, these collections form immensely valuable
    information sources for their work.
    These Web Archives contain snapshots of the Web sites
    at different points of time and are created by regularly
    crawling (parts of) the Web.

    With the number of archives increasing worldwide models,
    tools and techniques necessary to archive and index relevant
    parts of the web in order to create, retrieve and
    explore them in a meaningful way are being constantly suggested and developed.
    In our previous work\cite{fafalios2017SemLayer}, we proposed
    building semantic profiles/layers that describe information about
    the contents of the archived documents and could be used as a method to
    to solve the problem of archive exploration.
    Specifically, we used Semantic Web technologies as a base and
    constructed an RDF/S vocabulary that allowed for:
    a) describing useful metadata information about each archived
    document
    b) annotating each document with entities and events detected in its textual contents,
    c) enriching the detected entities/events\footnote{From now on,
        when we say \q{entities} we refer to both entities, events and concepts.} with more semantic information
    (like properties and related entities coming from the LOD), and
    d) publishing all this data on the Web in the standard RDF format
    (making thereby all this information directly accessible and exploitable by other systems and tools).
    The results showed that such semantic profiles/layers could meet complex information needs, especially {\em
    exploratory search} needs \cite{marchionini2006exploratory}.


    Even though {\em entity-centric} SPARQL queries on such structured data layers
    return relevant results, a shortcoming is sometimes the
    large number of results that we get for the
    queries that we submit. Moreover, all the
    results are equally relevant to the submitted query.
    This leads to the problem of the user judging which results he
    would want to consider to be \q{more} important than other results.
    For example, in the case of a user querying a {\em
    news archive} asking for \q{articles of 1988 asking about members of the German Parliament}, an implicit preference of
    the user would be to get those articles which might:
    a) have mentions of several members in the same article,
    b) have
    mentions of more prominent members to that time period rather than less prominent ones, and/or,
    c) contain members involved in significant events which happened during the time period.
    Thus, having algorithms to judge articles and return
    them in a ranked order would be useful for the user.


    To rank results, we propose ranking algorithms
    that take into account temporal aspects of entities, inter-relations
    between entities and relatedness of documents to entities.
    Our approach only exploits the data of the semantic repository
    (triples in RDF format) and thus
    can produce ranking at query-execution time.
    We based these algorithms by modelling the solutions of the
    following three problems:
    a) how to rank {\em documents} related to a time
    period and one or more entities,
    for example, articles mentioning former US President
    Barack Obama announcing a Nuclear Deal with Iran would be considered
    more important than him addressing the
    116th National Convention of the Veterans of Foreign Wars in Pittsburgh, PA,
    with both events having occurred in July 2015;
    b) how to rank {\em entities} related to a time period and one or more other
    entities, for example,
    Brexit is a more important entity related to former British Prime Minister David Cameron than American Intervention in Syria in 2016
    as he had to tender his resignation
    following the results of the Brexit polls;
    c) how to rank {\em time periods} related to one or more entities,
    for example, the period of September 2015 was a more
    significant period for the EU Chancellor Angela Merkel
    than July 2015 as the decision she made on letting trains filled with migrants enter Germany in during that time period led to a significant drop in her approval ratings\cite{merkel_rating}.


    We then evaluate whether our algorithms effectively solve these problems
    by running 20 {\em entity-centric} queries on a semantic layer of the {\em New York Times}
    archive and checking the result ranking against human relevance judgements to see which
    combination of the modelled factors leads to the best ranking.
====}

The rest of the paper is organized as follows:
Section \ref{sec:motivAndRW} motivates our work and presents related literature.
Section \ref{sec:queryingSemLayer} presents \new{basic} algorithms for ranking documents, entities, and time periods.
\new{Section \ref{sec:pagerank} tries to describe a probabilistic approach for the problem at hand.}
Section \ref{sec:eval} evaluates the algorithms and their combinations.
Finally, Section \ref{sec:concl} concludes the paper and
presents interesting directions for future research.




%=====================================================

\section{Background and Related Works (DRAFT)}
\label{sec:motivAndRW}

\input{semlayer_ranking_rw}

%=====================================================

\section{Ranking Documents for Structured Queries}
\label{sec:queryingSemLayer}

\input{semlayer_ranking_approach}

%=====================================================

\section{Stochastic Processing}
\label{sec:pagerank}

\input{semlayer_ranking_approach_pagerank}

%=====================================================

\section{Evaluation}
\label{sec:eval}

\input{semlayer_ranking_evaluation}

%=====================================================


\section{Conclusion}
\label{sec:concl}

We have introduced a model for ranking articles returned by running advanced
queries over semantic layers built by annotating an archived collection of
records. This approach has the important characteristic
that it can be directly applied at query-execution time since
it only exploits the data of the semantic layer(i.e., its RDF triples).
The defined model can be used to rank documents mentioning all(or some)
of the entities requested in the and takes the factors of inter-relations between entities,
document relatedness to the entities and temporal aspects of the entities into account.
The evaluation of the rankings produced by the model against human relevance judgements
show that by effectively combining the above mentioned factors our model can yield a good
ranking of the documents thus saving the user time in judging important results among
a collection of (nearly all) relevant results.

Regarding future work and research, extensions of our ranking approach
for semantic layers over versioned archives or over social media archives
could be developed. Another interesting direction would be to build
a user-friendly interactive interface which transparently transforms user
interactions to SPARQL queries(e.g., a faceted browsing interface)
allowing users to easily and effectively explore digital archives.


\subsection*{Acknowledgements}
The work was partially funded by the European Commission
for the ERC Advanced Grant ALEXANDRIA under grant No. 339233.


\bibliographystyle{abbrv}
\bibliography{bib/semlayerRanking}


\end{document}
